---
title: "HTR violin & dot plots — hier subclass"
author: "SawchukS"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  eval      = TRUE,
  message   = FALSE,
  warning   = FALSE,
  cache     = TRUE,
  fig.align = "center",
  out.width = "100%"
)

library(Seurat)
library(ggplot2)
library(patchwork)
library(dplyr)
library(headBCI)
library(proj5HT)
```

## Purpose

A single, clean source of violin and dot plots of serotonin receptor (HTR)
expression across cortical subclasses, replacing the scattered `Seurat-*`
Rmds (`Seurat-Figure.Rmd`, `Seurat-PatchSeqFigures.Rmd`,
`Seurat-Figures-offPipeline.Rmd`, `Seurat-Figures-depthHTR.Rmd`,
`Seurat-offPipeline-PatchSeqFigures.Rmd`, `Seurat-10xFigures.Rmd`).

**Grouping variable**

* **PatchSeq objects** (off-pipeline + on-pipeline macaque/human) are grouped
  by a per-cell **subclass identity with a documented fallback chain**:
  1. `hier_subclass_assignment` (canonical headBCI hier classifier, joined
     from `headBCI::sheets$cleanMD` via `proj5HT::add_hier_to_seurat()`),
  2. `subclass_Corr_label` (legacy correlation-based call — used today for
     the human PatchSeq cohort which is not yet in the hier classifier),
  3. `subclass_label` (raw AIBS taxonomy label).

  All three are space-normalised via `proj5HT::normalize_taxonomy_labels()`
  / `proj5HT::normalize_hier_assignments()` so the underscored vocabulary
  (`"L2/3_IT"`, `"L5_ET"`, …) is shared across every panel. A per-cohort
  `subclass_source` table below makes the fallback explicit.
* **10x reference objects** (`*MTG_10xFACs.rds`) are *not* in `cleanMD`
  (they have no `cell_name`), so they remain grouped by their native
  `subclass_label` — which is normalised to the underscored hier
  convention (`"L5 ET"` → `"L5_ET"`) at Seurat-object build time via
  `proj5HT::normalize_taxonomy_labels()`, so axis text matches the
  PatchSeq panels with no per-Rmd massaging.

This is the migration off `subclass_Corr` (correlation-only) /
`subclass_Tree` (legacy tree mapping) onto `hier_*_assignment` as the sole
project-wide subclass identity.

---

## Config

```{r config}
SEURAT_DIR <- "~/proj5HT/data-raw/Seurat"

## ---- receptor groupings (must mirror data-raw/build_htr_scores.R) ----------
HTR1     <- c("HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F")
HTR2     <- c("HTR2A", "HTR2B", "HTR2C")
HTR0     <- c("HTR4",  "HTR5A", "HTR6",  "HTR7")
HTR_ALL  <- c(HTR1, HTR2, HTR0)

## ---- subclass ordering (consistent across all panels) ----------------------
SUBCLASS_ORDER <- c(
  "L2/3_IT", "L4_IT", "L5_IT", "L6_IT", "L6_IT_Car3",
  "L5_ET", "L5/6_NP", "L6_CT", "L6b",
  "Pvalb", "Sst", "Sst_Chodl", "Vip", "Lamp5", "Lamp5_Lhx6", "Sncg", "Pax6"
)

## ---- shared plot decoration ------------------------------------------------
legend_guides <- guides(
  size  = guide_legend(title  = "% Exp"),
  color = guide_colorbar(title = "Avg Exp")
)
dot_cols   <- c("white", "blue")
dot_theme  <- theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r helpers}
## Drop unused factor levels and impose the canonical subclass order, keeping
## any unexpected subclass values at the end so nothing is silently dropped.
order_subclass <- function(x, levels = SUBCLASS_ORDER) {
  extra <- setdiff(unique(stats::na.omit(x)), levels)
  factor(x, levels = c(levels, extra))
}

## Make 10x `subclass_label` (e.g. "L2/3 IT") match hier convention (underscores)
## Kept here as a defensive fallback for older Seurat objects built before
## `proj5HT::normalize_taxonomy_labels()` was wired into the builder.
to_hier_style <- function(x) gsub(" ", "_", x, fixed = TRUE)

## Resolve a per-cell subclass identity with a documented fallback chain:
##   1. hier_subclass_assignment      (canonical, headBCI hier classifier)
##   2. subclass_Corr_label           (legacy correlation-based call)
##   3. subclass_label                (raw AIBS taxonomy label)
## Returns a list with `value` (character vector) and `source` (per-cell tag)
## so panels can declare which call they're plotting.
resolve_subclass <- function(obj) {
  md <- obj@meta.data
  hier <- md$hier_subclass_assignment
  corr <- md$subclass_Corr_label
  rawl <- md$subclass_label
  pick <- function(h, c, r) {
    if (!is.na(h) && nzchar(h)) return(c(value = h,    source = "hier"))
    if (!is.na(c) && nzchar(c)) return(c(value = c,    source = "subclass_Corr"))
    if (!is.na(r) && nzchar(r)) return(c(value = r,    source = "subclass_label"))
    c(value = NA_character_, source = NA_character_)
  }
  if (is.null(hier)) hier <- rep(NA_character_, ncol(obj))
  if (is.null(corr)) corr <- rep(NA_character_, ncol(obj))
  if (is.null(rawl)) rawl <- rep(NA_character_, ncol(obj))
  ## USE.NAMES = FALSE: otherwise mapply uses the *values* of `hier` as
  ## column names of the resulting matrix, which Seurat's `$<-` then
  ## misinterprets as cell barcodes ("No cell overlap" / NA in name check).
  m <- mapply(pick, hier, corr, rawl, USE.NAMES = FALSE)
  list(value  = unname(to_hier_style(m["value",  ])),
       source = unname(m["source", ]))
}

## Standard dot plot for a receptor family.
htr_dotplot <- function(obj, features, group.by, title,
                        scale = FALSE, scale.max = 100) {
  Seurat::DotPlot(
    object    = obj,
    features  = features,
    group.by  = group.by,
    scale     = scale,
    scale.min = 0,
    scale.max = scale.max,
    cols      = dot_cols
  ) +
    legend_guides +
    dot_theme +
    ggtitle(title)
}

## Stacked violin: one row per feature, shared x-axis (group).
htr_vlnstack <- function(obj, features, group.by, title) {
  Seurat::VlnPlot(
    object       = obj,
    features     = features,
    group.by     = group.by,
    pt.size      = 0,
    stack        = TRUE,
    flip         = TRUE,
    same.y.lims  = FALSE
  ) +
    ggtitle(title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
}
```

---

## Load objects

```{r load}
load_rds <- function(name) {
  p <- file.path(SEURAT_DIR, name)
  if (!file.exists(p)) { warning("missing: ", p); return(NULL) }
  readRDS(p)
}

## ---- PatchSeq (off-pipeline; canonical for hier comparisons) ---------------
mPatch <- load_rds("offPipeline-Macaque_PatchSeq.rds")
hPatch <- load_rds("offPipeline-Human_PatchSeq.rds")

## ---- 10x reference (no cell_name → no hier; use subclass_label) ------------
mMTG <- load_rds("MacaqueMTG_10xFACs.rds")
hMTG <- load_rds("HumanMTG_10xFACs.rds")
cMTG <- load_rds("ChimpMTG_10xFACs.rds")
gMTG <- load_rds("GorillaMTG_10xFACs.rds")
```

```{r attach-hier}
## Attach hier_* metadata to PatchSeq objects (idempotent — safe to re-run).
if (!is.null(mPatch)) mPatch <- proj5HT::add_hier_to_seurat(mPatch)
if (!is.null(hPatch)) hPatch <- proj5HT::add_hier_to_seurat(hPatch)
```

```{r prep-grouping}
## PatchSeq: prefer hier_subclass_assignment; fall back to subclass_Corr_label
## then subclass_label (human PatchSeq is not yet in the hier classifier).
stamp_subclass <- function(obj) {
  if (is.null(obj)) return(NULL)
  r <- resolve_subclass(obj)
  obj$subclass_hier   <- order_subclass(r$value)
  obj$subclass_source <- r$source
  obj
}
mPatch <- stamp_subclass(mPatch)
hPatch <- stamp_subclass(hPatch)

## 10x reference: subclass_label is already normalised at build time via
## `proj5HT::normalize_taxonomy_labels()`. Defensive `to_hier_style()` here
## keeps older Seurat objects (built before that wiring) consistent.
for (nm in c("mMTG", "hMTG", "cMTG", "gMTG")) {
  obj <- get(nm)
  if (is.null(obj)) next
  obj$subclass_hier   <- order_subclass(to_hier_style(obj$subclass_label))
  obj$subclass_source <- ifelse(is.na(obj$subclass_hier), NA_character_, "subclass_label")
  assign(nm, obj)
}
```

```{r subclass-source-table}
## Show which call (hier / subclass_Corr / subclass_label) is sourcing the
## grouping for each PatchSeq cohort — makes the fallback explicit.
src_tbl <- function(obj, name) {
  if (is.null(obj)) return(NULL)
  tibble::tibble(dataset = name,
                 source  = obj$subclass_source) |>
    dplyr::count(dataset, source)
}
dplyr::bind_rows(
  src_tbl(mPatch, "macaque_PatchSeq"),
  src_tbl(hPatch, "human_PatchSeq")
) |>
  tidyr::pivot_wider(names_from = source, values_from = n, values_fill = 0L) |>
  knitr::kable(caption = "PatchSeq subclass source (per-cell, after fallback)")
```

```{r subclass-counts}
## quick sanity table — how many cells per subclass per dataset
count_subclass <- function(obj, name) {
  if (is.null(obj)) return(NULL)
  tibble::tibble(dataset = name,
                 subclass = as.character(obj$subclass_hier)) |>
    dplyr::count(dataset, subclass)
}
dplyr::bind_rows(
  count_subclass(mPatch, "macaque_PatchSeq"),
  count_subclass(hPatch, "human_PatchSeq"),
  count_subclass(mMTG,   "macaque_10x"),
  count_subclass(hMTG,   "human_10x"),
  count_subclass(cMTG,   "chimp_10x"),
  count_subclass(gMTG,   "gorilla_10x")
) |>
  tidyr::pivot_wider(names_from = dataset, values_from = n, values_fill = 0L) |>
  knitr::kable(caption = "Cell counts per subclass × dataset")
```

---

## PatchSeq — violin plots (`hier_subclass_assignment`)

```{r vln-patchseq-macaque, fig.height = 6, fig.width = 9, eval = !is.null(mPatch)}
htr_vlnstack(mPatch, HTR_ALL, "subclass_hier",
             "Macaque PatchSeq — hier_subclass_assignment")
```

```{r vln-patchseq-human, fig.height = 6, fig.width = 9, eval = !is.null(hPatch)}
htr_vlnstack(hPatch, HTR_ALL, "subclass_hier",
             "Human PatchSeq — hier_subclass_assignment")
```

---

## PatchSeq — dot plots by family (`hier_subclass_assignment`)

```{r dot-patchseq, fig.height = 4, fig.width = 12, eval = !is.null(mPatch)}
(htr_dotplot(mPatch, HTR1, "subclass_hier", "Macaque HTR1") |
 htr_dotplot(mPatch, HTR2, "subclass_hier", "Macaque HTR2") |
 htr_dotplot(mPatch, HTR0, "subclass_hier", "Macaque other"))
```

```{r dot-patchseq-human, fig.height = 4, fig.width = 12, eval = !is.null(hPatch)}
(htr_dotplot(hPatch, HTR1, "subclass_hier", "Human HTR1") |
 htr_dotplot(hPatch, HTR2, "subclass_hier", "Human HTR2") |
 htr_dotplot(hPatch, HTR0, "subclass_hier", "Human other"))
```

---

## 10x reference — dot plots across species

Reference 10x FACS objects do not carry `cell_name`, so hier metadata is
not joined. Subclass labels here come from the native `subclass_label`
column (relabelled to underscored form for axis consistency).

```{r dot-10x-htr1, fig.height = 4, fig.width = 14, eval = !is.null(mMTG)}
(htr_dotplot(hMTG, HTR1, "subclass_hier", "Human 10x")   |
 htr_dotplot(mMTG, HTR1, "subclass_hier", "Macaque 10x") |
 htr_dotplot(cMTG, HTR1, "subclass_hier", "Chimp 10x")   |
 htr_dotplot(gMTG, HTR1, "subclass_hier", "Gorilla 10x"))
```

```{r dot-10x-htr2, fig.height = 4, fig.width = 14, eval = !is.null(mMTG)}
(htr_dotplot(hMTG, HTR2, "subclass_hier", "Human 10x")   |
 htr_dotplot(mMTG, HTR2, "subclass_hier", "Macaque 10x") |
 htr_dotplot(cMTG, HTR2, "subclass_hier", "Chimp 10x")   |
 htr_dotplot(gMTG, HTR2, "subclass_hier", "Gorilla 10x"))
```

```{r dot-10x-htr0, fig.height = 4, fig.width = 14, eval = !is.null(mMTG)}
(htr_dotplot(hMTG, HTR0, "subclass_hier", "Human 10x")   |
 htr_dotplot(mMTG, HTR0, "subclass_hier", "Macaque 10x") |
 htr_dotplot(cMTG, HTR0, "subclass_hier", "Chimp 10x")   |
 htr_dotplot(gMTG, HTR0, "subclass_hier", "Gorilla 10x"))
```

---

## 10x reference — stacked violins

```{r vln-10x-macaque, fig.height = 6, fig.width = 8, eval = !is.null(mMTG)}
htr_vlnstack(mMTG, HTR_ALL, "subclass_hier", "Macaque 10x — subclass_label")
```

```{r vln-10x-human, fig.height = 6, fig.width = 8, eval = !is.null(hMTG)}
htr_vlnstack(hMTG, HTR_ALL, "subclass_hier", "Human 10x — subclass_label")
```

---

## L2/3 IT focus — clusters within subclass

For the L2/3 IT subclass specifically, drop down to `hier_cluster_assignment`
to inspect within-subclass heterogeneity.

```{r l23-clusters, fig.height = 5, fig.width = 10, eval = !is.null(mPatch)}
l23 <- subset(mPatch, subset = hier_subclass_assignment == "L2/3_IT")
l23$cluster_hier <- factor(l23$hier_cluster_assignment)

htr_dotplot(l23, HTR_ALL, "cluster_hier",
            "Macaque L2/3_IT — hier_cluster_assignment", scale = FALSE)
```

---

## Provenance

* Subclass grouping: `headBCI::sheets$cleanMD$hier_subclass_assignment`
  (joined via `proj5HT::add_hier_to_seurat()`).
* Label normalisation: `proj5HT::normalize_hier_assignments()` — see
  [vignettes/hier-metadata.Rmd](../vignettes/hier-metadata.Rmd).
* Receptor families: must remain in sync with
  [data-raw/build_htr_scores.R](../data-raw/build_htr_scores.R) and
  [manu/_shared/setup.R](../manu/_shared/setup.R).
* Replaces (do not edit further; archive when convenient):
  `Seurat-Figure.Rmd`, `Seurat-PatchSeqFigures.Rmd`,
  `Seurat-Figures-offPipeline.Rmd`, `Seurat-Figures-depthHTR.Rmd`,
  `Seurat-offPipeline-PatchSeqFigures.Rmd`,
  `Seurat-Figures-offPipeline_inhibitory.Rmd`.

```{r sessioninfo, echo = FALSE}
sessioninfo::session_info()
```
