---
title: "Seurat figures for off-pipeline data"
author: "SawchukS"
date: "2025-07-16"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      out.width = "100%",
                      warning = FALSE,
                      cache = TRUE)

library(metap)
library(feather)
library(Seurat)
library(ggplot2)

MD = projHCT::sheets$MD
cMD = projHCT::sheets$cleanMD

HTRgenesINT = c(
  "HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F", "HTR2A", "HTR2B", "HTR2C", "HTR4", "HTR5A", "HTR6", "HTR7"
)
HTRgenes12 = c("HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F", "HTR2A", "HTR2B", "HTR2C")
HTR1 = c("HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F")
HTR2 = c("HTR2A", "HTR2B", "HTR2C")
HTR0 = c("HTR4", "HTR5A", "HTR6", "HTR7")





```

# Setup capacity to compare with human data.

```{r include=FALSE}


brain = readRDS("~/proj5HT/data-raw/Seurat/offPipeline-Macaque_PatchSeq_excitatory.rds")
brainM = subset(brain, subset = Cortical_area %in% c("MCx"))
brain = subset(brain, subset = Cortical_area %in% c("TCx"))
brain$grouping = ifelse(brain$subclass_Corr %in% c("L4_IT", "L6_IT", "L5/6_NP", "L6b", "L6_CT", "L6_IT_Car3"), "group64", "group235")
brain64 = subset(brain, subset = grouping  %in% c("group64"))
brain = subset(brain, subset = grouping  %in% c("group235"))
brain$subclass = brain$subclass_Corr
brainM$subclass = brainM$subclass_Corr
brainM = subset(brainM, subset = subclass  %in% c("L2/3_IT", "L5_ET", "L5_IT"))

human = readRDS("~/proj5HT/data-raw/Seurat/offPipeline-Human_PatchSeq.rds")
human$subclass = human$subclass_Corr_label
human$subclass = as.character(gsub(" ", "_", human$subclass))
human = subset(human, subset = Cortical_area %in% c("TCx"))
unique(human$subclass)
human = subset(human, subset = subclass  %in% c("L2/3_IT", "L5_ET", "L5_IT"))

cMTG = readRDS("~/proj5HT/data-raw/Seurat/MacaqueMTG_10xFACs.rds")
cMTG$subclass_label = as.character(gsub(" ", "_", cMTG$subclass_label))
cMTG = subset(cMTG, subset = subclass_label  %in% c("L4_IT", "L6_IT", "L5/6_NP", "L6b", "L6_CT", "L6_IT_Car3", "L2/3_IT", "L5_ET", "L5_IT"))
cMTG$grouping = ifelse(cMTG$subclass_label %in% c("L4_IT", "L6_IT", "L5/6_NP", "L6b", "L6_CT","L6_IT_Car3"), "group64", "group235")
cMTG = subset(cMTG, subset = grouping  %in% c("group235"))
cMTG$subclass = cMTG$subclass_label


hMTG = readRDS("~/proj5HT/data-raw/Seurat/HumanMTG_10xFACs.rds")
hMTG$subclass_label = as.character(gsub(" ", "_", hMTG$subclass_label))
hMTG$subclass = hMTG$subclass_label
hMTG = subset(hMTG, subset = subclass  %in% c("L2/3_IT", "L5_ET", "L5_IT"))


chimpMTG = readRDS("~/proj5HT/data-raw/Seurat/ChimpMTG_10xFACs.rds")
chimpMTG = subset(chimpMTG, subset = subclass_label  %in% c("L2/3_IT", "L5_ET", "L5_IT"))
chimpMTG$subclass = chimpMTG$subclass_label


gMTG = readRDS("~/proj5HT/data-raw/Seurat/GorillaMTG_10xFACs.rds")
gMTG = subset(gMTG, subset = subclass_label  %in% c("L2/3_IT", "L5_ET", "L5_IT"))
gMTG$subclass = gMTG$subclass_label


```

## Figures
Combined shows nCount_RNA being far from each other
```{r, eval = TRUE}
VlnPlot(brain, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), group.by = "set", ncol = 3)
```

## Violin plots Without Normalizing the data
```{r, fig.height=15, fig.width=12}
VlnPlot(brain, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass", same.y.lims = TRUE)
VlnPlot(cMTG, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass_label", same.y.lims = TRUE)
VlnPlot(hMTG, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass_label", same.y.lims = TRUE)
```

```{r, fig.height=4, fig.width=10}
VlnPlot(brain, features = HTR1, pt.size = 0.2, ncol = 5, group.by = "subclass",layer = "counts", same.y.lims = TRUE)
```

```{r, fig.height=4, fig.width=6}
VlnPlot(brain, features = HTR2, pt.size = 0.2, ncol = 3, group.by = "subclass", layer = "counts", same.y.lims = TRUE)
```

```{r, fig.height=4, fig.width=8}
VlnPlot(brain, features = HTR0, pt.size = 0.2, ncol = 4, group.by = "subclass", layer = "counts", same.y.lims = TRUE)
```


## Dotplot helper

```{r}
library(cowplot)
library(ggplot2)

dot_theme <- theme(
  axis.text.x = element_text(angle = 45, hjust = 1),
  axis.title = element_blank(),
  plot.margin = margin(2, 2, 2, 2),     # tighter gutters
  legend.position = "right"
)

make_dot <- function(obj, features, title = NULL,
                     colours = c("lightgrey", "blue"),
                     limits = c(0, 10),
                     oob = scales::squish) {

  Seurat::DotPlot(
    object  = obj,
    features = features,
    group.by = "subclass",
    scale   = FALSE
  ) +
    ggplot2::scale_x_discrete(drop = FALSE) +
    ggplot2::scale_colour_gradientn(
      colours = colours,
      limits  = limits,
      oob     = oob
    ) +
    ggplot2::guides(legend_guides) +
    ggplot2::ggtitle(title) +
    dot_theme
}


make_dot <- function(obj, features, title = NULL, colours = c("white", "blue")) {
  DotPlot(
    object = obj,
    features = features,
    group.by = "subclass",
    scale = FALSE,
    cols = colours
  ) +
    scale_x_discrete(drop = FALSE) +
    guides(legend_guides) +
    range_colour +
    ggtitle(title) +
    dot_theme
}

# Build plots (NO legends in-grid)
p1 <- make_dot(hMTG,     HTR1, "Human TCx 10x") + theme(legend.position="none")
p2 <- make_dot(cMTG,     HTR1, "Macaque TCx 10x") + theme(legend.position="none")
p3 <- make_dot(chimpMTG, HTR1, "Chimp TCx 10x") + theme(legend.position="none")
p4 <- make_dot(gMTG,     HTR1, "Gorilla TCx 10x") + theme(legend.position="none")

p5 <- make_dot(hMTG,     HTR2, "Human TCx 10x") + theme(legend.position="none")
p6 <- make_dot(cMTG,     HTR2, "Macaque TCx 10") + theme(legend.position="none")
p7 <- make_dot(chimpMTG, HTR2, "Chimp TCx 10x") + theme(legend.position="none")
p8 <- make_dot(gMTG,     HTR2, "Gorilla TCx 10x") + theme(legend.position="none")

p6 <- make_dot(hMTG,     HTR0, "Human TCx 10x") + theme(legend.position="none")
p10 <- make_dot(cMTG,     HTR0, "Macaque TCx 10") + theme(legend.position="none")
p11 <- make_dot(chimpMTG, HTR0, "Chimp TCx 10x") + theme(legend.position="none")
p12 <- make_dot(gMTG,     HTR0, "Gorilla TCx 10x") + theme(legend.position="none")

p13 <- make_dot(human,     HTR2, "Human TCx Patch-seq", colours = c("white", "red")) + theme(legend.position="none") 
p14 <- make_dot(brain,     HTR2, "Macaque TCx Patch-seq", colours = c("white", "red")) + theme(legend.position="none")

p15 <- make_dot(human,     HTR1, "Human TCx Patch-seq", colours = c("white", "red")) + theme(legend.position="none") 
p16 <- make_dot(brain,     HTR1, "Macaque TCx Patch-seq", colours = c("white", "red")) + theme(legend.position="none")


```

## Legends
```{r}
# Make ONE legend (from any representative plot)
p_leg <- make_dot(cMTG, HTR2, " ") +
  theme(
    plot.title = element_blank(),
    legend.box.margin = margin(0,0,0,0),
    legend.margin = margin(0,0,0,0)
  )
leg_mac10x <- get_legend(p_leg)
p_leg2 <- make_dot(brain, HTR2, " ", colours = c("white", "red")) +
  theme(
    plot.title = element_blank(),
    legend.box.margin = margin(0,0,0,0),
    legend.margin = margin(0,0,0,0)
  )
leg_macPatch <- get_legend(p_leg2)
```

```{r}
mac10x_with_leg <- plot_grid(
  p6, leg_mac10x,
  ncol = 2,
  rel_widths = c(1, 0.18)
)

macPatch_with_leg <- plot_grid(
  p14, leg_macPatch,
  ncol = 2,
  rel_widths = c(1, 0.18)
)

tenX = plot_grid(
  p5,
  mac10x_with_leg,
  ncol = 2,
  rel_widths = c(1, 1.22)   # shrink legend column; tune 0.08–0.18
  )
p_PS = plot_grid(
  p13,
  macPatch_with_leg,
  ncol = 2,
  rel_widths = c(1, 1.22)   # shrink legend column; tune 0.08–0.18
  )

plot_grid(
  tenX, p_PS,
  ncol = 1,
  rel_widths = c(1, 1)   # shrink legend column; tune 0.08–0.18
)


```

```{r}
mac10x_with_leg <- plot_grid(
  p2, leg_mac10x,
  ncol = 2,
  rel_widths = c(1, 0.18)
)

macPatch_with_leg <- plot_grid(
  p16, leg_macPatch,
  ncol = 2,
  rel_widths = c(1, 0.18)
)

tenX = plot_grid(
  p1,
  mac10x_with_leg,
  ncol = 2,
  rel_widths = c(1, 1.22)   # shrink legend column; tune 0.08–0.18
  )
p_PS = plot_grid(
  p15,
  macPatch_with_leg,
  ncol = 2,
  rel_widths = c(1, 1.22)   # shrink legend column; tune 0.08–0.18
  )

plot_grid(
  tenX, p_PS,
  ncol = 1,
  rel_widths = c(1, 1)   # shrink legend column; tune 0.08–0.18
)


```

### Violins comparing Human to Macaque

```{r}
library(Seurat)
library(ggplot2)
library(cowplot)

vln_5plus_legend6 <- function(obj,
                              features,
                              title = NULL,
                              group.by = "subclass",
                              split.by = "species",
                              assay = "RNA",
                              slot = "counts",
                              split.plot = TRUE,
                              n_columns = NULL,
                              pt.size = 0) {
  DefaultAssay(obj) <- assay
  Idents(obj) <- group.by
  
  # 1) Make one plot per gene
  plist <- VlnPlot(
    obj,
    features = features,
    group.by = group.by,
    split.by = split.by,
    assay = assay,
    slot = slot,
    pt.size = pt.size,
    split.plot = split.plot,
    combine = FALSE,
    ncol = 3
  )
  
  # 2) Legend only on first plot (then extract)
  plist[[1]] <- plist[[1]] + theme(legend.position = "right")
  leg <- cowplot::get_legend(plist[[1]])
  
  # 3) Remove legends from all gene plots
  plist <- lapply(plist, \(p) p + theme(legend.position = "none"))
  
  # 4) Create a blank panel to hold the legend (slot 6)
  leg_panel <- cowplot::ggdraw(leg)
  
  # 5) Arrange 3x2: first 5 genes + legend in 6th
  grid <- cowplot::plot_grid(
    plotlist = c(plist, list(leg_panel)),
    ncol = n_columns,
    align = "hv",
    axis = "tblr"
  )
  
  # Optional title
  if (!is.null(title)) {
    grid <- cowplot::plot_grid(
      cowplot::ggdraw() + cowplot::draw_label(title, fontface = "bold", x = 0, hjust = 0),
      grid,
      ncol = 1,
      rel_heights = c(0.08, 1)
    )
  }
  
  grid
}

#combined_10x   <- subset(combined, subset = method == "10x")
#combined_patch <- subset(combined, subset = method == "Patch-seq")

p_patch <- vln_5plus_legend6(combined_patch, HTR1, title = "Patch-seq", n_columns = 3)
p_10x   <- vln_5plus_legend6(combined_10x,   HTR1, title = "10x", n_columns = 3)
p_10x / p_patch


p_patch2 <- vln_5plus_legend6(combined_patch, HTR2, title = "Patch-seq", n_columns = 4)
p_10x2   <- vln_5plus_legend6(combined_10x,   HTR2, title = "10x", n_columns = 4)

p_10x2 / p_patch2


```




## Assemblage
```{r}
# Tight plot grid (same sizing, no legend space)
grid1 <- plot_grid(
  p1,p2,p3,p4,
  #p5,p6,p7,p8,
  ncol = 4,
  align = "hv",
  axis = "tblr"
)

grid2 <- plot_grid(
  #p1,p2,p3,p4,
  p5,p6,p7,p8,
  ncol = 4,
  align = "hv",
  axis = "tblr",labels = "auto"
)
    
gridMH <- plot_grid(
  p5,p6,p13,p14,
  ncol = 4,
  align = "hv",
  axis = "tblr",labels = "auto"
)
plot_grid(
  gridMH, leg,
  ncol = 2,
  rel_widths = c(1, 0.12)   # shrink legend column; tune 0.08–0.18
)


# Combine grid + legend with controlled relative widths
plot_grid(
  grid1, leg,
  ncol = 2,
  rel_widths = c(1, 0.12), # shrink legend column; tune 0.08–0.18
  
)

plot_grid(
  grid2, leg,
  ncol = 2,
  rel_widths = c(1, 0.12)   # shrink legend column; tune 0.08–0.18
)

plot_grid(
  gridMH, leg,
  ncol = 2,
  rel_widths = c(1, 0.12)   # shrink legend column; tune 0.08–0.18
)

```

### Macaque and Human comparison of 

```{r fig.dims = c(4,4)}
p6 <- make_dot(hMTG,     HTR0, "Human TCx 10x") + theme(legend.position="none")
p10 <- make_dot(cMTG,     HTR0, "Macaque TCx 10") + theme(legend.position="none")
p11 <- make_dot(chimpMTG, HTR0, "Chimp TCx 10x") + theme(legend.position="none")
p12 <- make_dot(gMTG,     HTR0, "Gorilla TCx 10x") + theme(legend.position="none")


grid.arrange(
  DotPlot(
    object = hMTG,
    features = HTR2,
    group.by = "subclass_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10x"),
  DotPlot(
    object = cMTG,
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Macaque TCx 10x"),
  DotPlot(
    object = subset(human, subset = Cortical_area %in% c("TCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("Macaque TCx Smartseq"),
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("TCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("Macaque TCx Smartseq"),
  ncol = 4
)
```




```{r, fig.height=8, fig.width=10, eval =FALSE}
DotPlot(object = brain, features = HTR1, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

```{r, fig.height=8, fig.width=6, eval =FALSE}
DotPlot(object = brain, features = HTR2, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

```{r, fig.height=8, fig.width=8, eval =FALSE}
DotPlot(object = brain, features = HTR0, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

## Dotplots
```{r, fig.height=4, fig.width=8, eval =TRUE}
DotPlot(object = brain, features = HTRgenesINT, group.by = "subclass", scale = FALSE) + guides(legend_guides) + ggtitle("Smart-Seq Patch-Seq")

#subset(brain, subset = Cortical_area %in% c("TCx", "MCx")) %>% 
DotPlot(object = subset(brain, subset = Cortical_area %in% c("MCx")), features = HTRgenesINT, group.by = "subclass", scale = FALSE, cols = "blue") + guides(legend_guides) + range_colour + ggtitle("MCx")

DotPlot(object = subset(brain, subset = Cortical_area %in% c("TCx")), features = HTRgenesINT, group.by = "subclass", scale = FALSE, cols = "red") + guides(legend_guides) + range_colour + ggtitle("TCx")


```

# Cortical area separated dotplots
```{r fig.dim=c(6,12)}

grid.arrange(
  DotPlot(
    brainM,
    features = HTRgenesINT,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + range_colour + ggtitle("MCx"),
  DotPlot(
    brain,
    features = HTRgenesINT,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + range_colour +ggtitle("TCx"),
  ncol = 2
)
```


```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("MCx")),
    features = HTR1,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("MCx"),
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("TCx")),
    features = HTR1,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("TCx"),
  ncol = 2
)
```


# 5HT2

### Offpipeline MCx vs TCx 

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("MCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("MCx"),
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("TCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("TCx"),
  ncol = 2
)
```


### Offpipeline TCx vs Human 10x FACs

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = hMTG,
    features = HTR2,
    group.by = "subclass_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10xFACs"),
  DotPlot(
    object = cMTG,
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Macaque TCx 10xFACs"),
  ncol = 2
)

```

### Macaque and Human comparison of 

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = hMTG,
    features = HTR2,
    group.by = "subclass_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10x"),
  DotPlot(
    object = cMTG,
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Macaque TCx 10x"),
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("TCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("Macaque TCx Smartseq"),
  ncol = 3
)

```



# HTR1
### Offpipeline MCx vs TCx 

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("MCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "red")
  ) + guides(legend_guides) + ggtitle("MCx"),
  DotPlot(
    object = subset(brain, subset = Cortical_area %in% c("TCx")),
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("TCx"),
  ncol = 2
)
```


### Offpipeline TCx vs Human 10x FACs

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = hMTG,
    features = HTR2,
    group.by = "subclass_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10xFACs"),
  DotPlot(
    object = cMTG,
    features = HTR2,
    group.by = "subclass",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Macaque TCx 10xFACs"),
  ncol = 2
)

```


## Plot Cluster types 

### L2/3 IT cluster types

```{r}
VlnPlot(object = subset(brain, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster")
```

```{r}

grid.arrange(
DotPlot(object = subset(brain, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID Smart-Seq Patch-Seq"),
DotPlot(object = subset(cMTG, subset = subclass_label %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID fo 10x-FACs data"),
nrow = 2
)
```

```{r}

brain2 = subset(brain, subset = Cortical_area %in% "TCx")

grid.arrange(
DotPlot(object = subset(brain2, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID Smart-Seq Patch-Seq"),
DotPlot(object = subset(brain2, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID Smart-Seq Patch-Seq"),
#DotPlot(object = subset(cMTG, subset = subclass_label %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID fo 10x-FACs data"),
#DotPlot(object = subset(cMTG, subset = subclass_label %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID fo 10x-FACs data"),
nrow = 2
)
```

### L5 ET cluster types

```{r}
VlnPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster")
```

```{r}
DotPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides)
```

```{r}

grid.arrange(
DotPlot(object = subset(cMTG, subset = subclass_label %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID fo 10x-FACs data"),
DotPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID Smart-Seq Patch-Seq"),
nrow = 2
)
```
