---
title: "Seurat figures for off-pipeline data"
author: "SawchukS"
date: "2025-07-16"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      out.width = "100%",
                      warning = FALSE,
                      cache = TRUE)

library(metap)
library(feather)
library(Seurat)
library(ggplot2)

MD = projHCT::sheets$MD
cMD = projHCT::sheets$cleanMD

HTRgenesINT = c(
  "HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F", "HTR2A", "HTR2B", "HTR2C", "HTR4", "HTR5A", "HTR6", "HTR7"
)
HTRgenes12 = c("HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F", "HTR2A", "HTR2B", "HTR2C")
HTR1 = c("HTR1A", "HTR1B", "HTR1D", "HTR1E", "HTR1F")
HTR2 = c("HTR2A", "HTR2B", "HTR2C")
HTR0 = c("HTR4", "HTR5A", "HTR6", "HTR7")

legend_guides = c(size = guide_legend(title = "% Exp"), color = guide_colorbar(title = "Avg Exp"))
```

## if you’re working with Allen Brain Atlas single-cell references, subclass_Corr is the correlation-based direct subclass assignment, while subclass_Tree is the hierarchical tree-based subclass assignment that mirrors their cell type taxonomy.


### subclass_Corr labeling
    Method: Based on correlation to reference expression profiles. 
    A cell’s transcriptome is compared (often via Pearson/Spearman correlation or cosine similarity) to reference profiles for known subclasses.
    The best-correlated subclass is assigned.
    Pros:
        Simple, quantitative, interpretable.
        Works well if your data matches the reference in technical profile.
    Cons:
        Can be misled by batch effects or global shifts.
        Doesn’t enforce hierarchical relationships — the best match could be biologically implausible if the correlation is skewed.

### subclass_Tree labeling
    Method: Based on hierarchical decision tree classification.
    The annotation proceeds step-by-step:
        First, broad class is identified (e.g., excitatory neuron vs inhibitory neuron vs glia).
        Then, within that class, the algorithm refines to a subclass (e.g., L2/3 IT vs L5 ET).
    This is often implemented as a series of marker-based or trained binary classifiers at each node in the tree.
    Pros:
        Respects biological hierarchy.
        Reduces risk of “jumping” to an unrelated subclass.
    Cons:
        If an early branch is misclassified, all downstream labels will be wrong.
        Performance depends on the quality of markers at each decision split.

# Off-pipeline

```{r op-PatchSeq SeuratObjects, include=FALSE}
hopPS = readRDS("~/proj/proj5HT/data-raw/Seurat/offPipeline-Human_PatchSeq.rds")
table(hopPS$subclass_Corr_label)
# Select only the temporal cortex for these data
hopPS = subset(hopPS, subset = Cortical_area %in% c('TCx'))
#hopPS = subset(hopPS, subset = subclass_Corr_label %in% c('L5 IT','L5 ET',"L2/3 IT"))
# Separate L6 cells from L5IT,L5ET, and L2/3IT
# hopPS6 = subset(hopPS, subset = subclass_Corr_label %in% c('L6 IT','L6b',"L6 CT"))

mopPS = readRDS("~/proj/proj5HT/data-raw/Seurat/offPipeline-Macaque_PatchSeq.rds")
# Data Descriptors
table(mopPS$subclass_Corr_label)
#table(mopPS$subclass_Tree_label)
table(mopPS$Cortical_area)

# Select only the temporal and motor corticies for these data
mopPS = subset(mopPS, subset = Cortical_area %in% c('TCx', "MCx"))
# Separate L6 cells from L5IT,L5ET, and L2/3IT
#mopPS6 = subset(mopPS, subset = subclass_Corr_label %in% c('L6 IT','L6b',"L6 CT"))
#mopPS = subset(mopPS, subset = subclass_Corr_label %in% c('L5 IT','L5 ET',"L2/3 IT"))

# New Data Descriptors
table(mopPS$subclass_Corr_label)
table(mopPS$Cortical_area)


```

## Describe the N for each group. 

```{r fig.dims = c(4,4)}
# TODO Make figure for desciribing number of cells from each region once paired down.

df = data.frame(subclass = c(mopPS$subclass_Corr_label,hopPS$subclass_Corr_label), prep = c(mopPS$species_label, hopPS$species_label))

table(df$prep)

ggplot(df, aes(x = subclass, fill = prep)) +
  geom_bar() +
  theme_minimal()

```


# 5HT2

### Human vs Macaque
Very little data from the human dataset when selecting for TCx only

```{r fig.dims = c(4,4)}
unique(hopPS$Cortical_area)
unique(mopPS$Cortical_area)
table(mopPS$subclass_Corr_label)

grid.arrange(
  DotPlot(
    object = hopPS,
    features = HTR2,
    group.by = "subclass_Corr_label",
    #split.by = "Cortical_area",
    scale = FALSE,
        scale.min = 0,
    scale.max = 100
    #cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human op Patch-Seq"),
  DotPlot(
    object = subset(mopPS, subclass_Corr_label = "TCx" ),
    features = HTR2,
    group.by = "subclass_Corr_label",
    #split.by = "Cortical_area",
    scale = FALSE,
        scale.min = 0,
    scale.max = 100
    #cols = c("white", "blue")
    ) + guides(legend_guides) + ggtitle("Macaque op Patch-Seq"),
  ncol = 2
)
```



# HTR1

### Comparison of HTR1 genes 

```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = hopPS,
    features = HTR1,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("HTR1 genes op-Human TCx Patch-Seq"),
  DotPlot(
    object = mopPS,
    features = HTR1,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
    ) + guides(legend_guides) + ggtitle("HTR1 genes op-Macaque TCx Patch-Seq"),
 ncol = 2
)

```


```{r fig.dims = c(4,4)}
grid.arrange(
  DotPlot(
    object = hopPS,
    features = HTR0,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10xFACs"),
  DotPlot(
    object = mopPS,
    features = HTR0,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
    ) + guides(legend_guides) + ggtitle("Macaque TCx 10xFACs"),
  DotPlot(
    object = cMTG,
    features = HTR0,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Chimp TCx 10xFACs"),
  DotPlot(
    object = gMTG,
    features = HTR0,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    scale.min = 0,
    scale.max = 100,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Gorilla TCx 10xFACs"),
  ncol = 4
)

```



```{r}
grid.arrange(
  DotPlot(
    object = hopPS,
    features = HTR2,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Human TCx 10x"),
  DotPlot(
    object = macMTG,
    features = HTR2,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Macaque TCx 10x"),
  DotPlot(
    object = cMTG,
    features = HTR2,
    group.by = "subclass_Corr_label",
    scale = FALSE,
    cols = c("white", "blue")
  ) + guides(legend_guides) + ggtitle("Chimp TCx 10x"),
  ncol = 3
)
```



```{r, fig.height=8, fig.width=10, eval =FALSE}
DotPlot(object = brain, features = HTR1, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

```{r, fig.height=8, fig.width=6, eval =FALSE}
DotPlot(object = brain, features = HTR2, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

```{r, fig.height=8, fig.width=8, eval =FALSE}
DotPlot(object = brain, features = HTR0, group.by = "subclass", scale = FALSE) + guides(legend_guides)
```

## Plot Cluster types 

### L2/3 IT cluster types

```{r}
VlnPlot(object = subset(brain, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster")
```

```{r}

grid.arrange(
DotPlot(object = subset(brain, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID Smart-Seq Patch-Seq"),
DotPlot(object = subset(cMTG, subset = subclass_Corr_label %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID fo 10x-FACs data"),
nrow = 2
)
```

```{r}

brain2 = subset(brain, subset = Cortical_area %in% "TCx")

grid.arrange(
DotPlot(object = subset(brain2, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID Smart-Seq Patch-Seq"),
DotPlot(object = subset(brain2, subset = subclass %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID Smart-Seq Patch-Seq"),
#DotPlot(object = subset(cMTG, subset = subclass_Corr_label %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID fo 10x-FACs data"),
#DotPlot(object = subset(cMTG, subset = subclass_Corr_label %in% "L2/3 IT"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L2/3 Cluster ID fo 10x-FACs data"),
nrow = 2
)
```

### L5 ET cluster types

```{r}
VlnPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster")
```

```{r}
DotPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides)
```

```{r}

grid.arrange(
DotPlot(object = subset(cMTG, subset = subclass_Corr_label %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID fo 10x-FACs data"),
DotPlot(object = subset(brain, subset = subclass %in% "L5 ET"), features = HTRgenesINT, group.by = "cluster", scale = FALSE) + guides(legend_guides) + ggtitle("L5 ET Cluster ID Smart-Seq Patch-Seq"),
nrow = 2
)
```

## Violin plots Without Normalizing the data
```{r, fig.height=15, fig.width=12}
#VlnPlot(mopPS, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass_Corr_label", same.y.lims = TRUE)
#VlnPlot(hopPS, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass_Corr_label", same.y.lims = TRUE)
#VlnPlot(hePS, features = HTRgenesINT, pt.size = 0.2, ncol = 4, group.by = "subclass_Corr_label", same.y.lims = TRUE)
```

