---
title: "proj5HT Plotting Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{proj5HT Plotting Functions}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 5,
  dpi = 150,
  out.width = "100%"
)
```

```{r setup, message = FALSE}
library(proj5HT)
library(projHCT)
library(ggplot2)
library(dplyr)
```

# Overview

`proj5HT` provides several families of plotting functions for visualizing
serotonin puff-response data:
 
| Function | Description |
|----------|-------------|
| `plot_cell_qc()` | Per-cell QC trace (raw + smoothed % baseline) |
| `plot_cell_qc_many()` | Batch-save QC traces to PNG |
| `plot_response_composition()` | Stacked bar of response classes by subclass |
| `plot_response_heatmap()` | Tile heatmap of response call vs subclass |
| `plot_centered_violin()` | Violin + jitter of response peak by subclass |
| `plot_exc_inh_traces()` | Faceted excitation/inhibition traces with group mean |
| `plotBasicPuff()` | Dual-axis puff trace (% change + firing rate) |
| `plotWashIn()` | Baseline vs drug wash-in comparison |
| `plot_asp_single_protocol()` | Single protocol trace + heat strip |
| `plot_asp_concatenated()` | Concatenated multi-protocol trace + heat strip |
| `plot_sidebyside_heat_wash()` | Side-by-side baseline vs wash heat plots |

This vignette walks through each family using real data.

---

# 1. Load data

All 5-HT plotting workflows start from either:

- A **compiled puff dataframe** (e.g. `compile_srtPuff.csv`) for the classifier
  plots, or
- An **srt nnest** (loaded via `load5HT()` / `loadHCT()`) for the ASP and
  protocol-level plots.

## 1a. Classifier pipeline data

The classifier plots consume `df_prepped` and `per_cell` — produced by the
`classify_puff_response()` pipeline.

```{r classifier-data, eval = FALSE}
# Load the compiled puff dataset
#comp <- readRDS("data-raw/compiled5HT.rds")

# Or read from CSV
comp <- read.csv("data-raw/compile_srtPuff.csv")

dfs = figure_df_build()

# Run the full classification pipeline
res <- classify_puff_response(dfs$df0)

df_prepped <- res$df_prepped
per_cell   <- res$per_cell
```

## 1b. Single-cell (srt) data

```{r}

```


Protocol-level plots use an srt nnest loaded from the rookery.

```{r srt-data, eval = FALSE}
#sh5HT <- sheets5HT()
#cells  <- sh5HT$nnested_cells
cells = proj5HT::sh5HT$nnested_cells

# Load a single cell
srt <- load5HT(cells[5], tag = "-srt.rds", rehydrate = FALSE)

# Ensure ASP is built
if (is.null(srt$dfs$asp)) {
  srt$dfs$asp <- build_asp(srt)
}
```

---

# 2. Classifier plots

These five functions from `plot_classify5HT.R` operate on the output of
`classify_puff_response()`.

## 2a. Per-cell QC trace — `plot_cell_qc()`

Shows the raw and smoothed `pct_of_baseline` trace for a single cell,
with shaded time-window bands and excursion threshold lines.

```{r qc-trace, eval = FALSE}
# Pick one cell
cell_id <- per_cell$cell_name[1]

p <- plot_cell_qc(df_prepped, cell_id = cell_id)
p
```

Key parameters:

- `smooth_method`: `"rollmean"` (default), `"rollmedian"`, or `"loess"`
- `smooth_k`: rolling window width (default 3)
- `rapid_window`, `mid_window`, `late_window`: shaded time bands
- `min_excursion_pct`: horizontal threshold lines at 100 ± this value

```{r qc-trace-custom, eval = FALSE}
# Customized version
plot_cell_qc(
  df_prepped,
  cell_id = cell_id,
  smooth_method = "loess",
  loess_span = 0.3,
  min_excursion_pct = 15
)
```

## 2b. Batch QC plots — `plot_cell_qc_many()`

Saves per-cell QC PNGs to a directory in one call.

```{r qc-many, eval = FALSE}
plot_cell_qc_many(
  df_prepped,
  cell_ids = per_cell$cell_name[1:5],
  out_dir  = "figs/qc",
  width    = 7,
  height   = 4.5,
  dpi      = 200
)
```

## 2c. Response composition — `plot_response_composition()`

Stacked bar chart showing the fraction of each response class within
each subclass.

```{r composition, eval = FALSE}
plot_response_composition(per_cell)
```

Change the grouping variable:

```{r composition-custom, eval = FALSE}
plot_response_composition(per_cell, x = "Species")
```

## 2d. Response heatmap — `plot_response_heatmap()`

A tile heatmap of response call vs subclass, with percentage labels.

```{r heatmap, eval = FALSE}
plot_response_heatmap(per_cell)
```

```{r heatmap-custom, eval = FALSE}
# Flip axes
plot_response_heatmap(per_cell, x = "assigned_subclass", y = "response_call")
```

## 2e. Violin plot — `plot_centered_violin()`

Violin + jitter showing `response_peak` by subclass, colored by direction.

```{r violin, eval = FALSE}
plot_centered_violin(per_cell)
```

## 2f. Excitation / inhibition traces — `plot_exc_inh_traces()`

Faceted panel showing individual cell traces (grey) with a bold group
mean, split by response type and subclass.

```{r exc-inh-traces, eval = FALSE}
plot_exc_inh_traces(
  df_prepped,
  per_cell,
  subclasses = c("L23_IT", "L5_ET", "L5_IT"),
  xlim       = c(-5, 60),
  smooth_k   = 3
)
```

---

# 3. Basic puff & wash-in plots

## 3a. Basic puff trace — `plotBasicPuff()`

Dual-axis plot (% change on left, firing rate on right) for a single srt
nnest's `spikeTTL` output.

```{r basic-puff, eval = FALSE}
plotBasicPuff(srt, bin_seconds = 1, xlim = c(-20, 50))
```

## 3b. Wash-in comparison — `plotWashIn()`

Overlays baseline and drug wash-in conditions with faceted panels for
firing rate and percent change.

```{r wash-in, eval = FALSE}
plotWashIn(srt, bin_seconds = 1, xlim = c(-20, 60))
```

---

# 4. ASP protocol plots

The ASP (All Spike Puff) system produces protocol-level views of the
firing-rate response with a companion heat strip.

## 4a. Single protocol — `plot_asp_single_protocol()`

Plots one protocol section: a trace panel (points colored by instRate)
and a one-row heat strip.

```{r asp-single, eval = FALSE}
asp <- srt$dfs$asp

# By exact key
plot_asp_single_protocol(asp, protocol_key = names(asp$by_protocol)[1], x_lim = c(-15, 40), heat_dt = 2)

# By regex match
plot_asp_single_protocol(asp, key_match = "standard_puff", y_mode = "log2_fc",, x_lim = c(-15, 40), heat_dt = 2)
```

Available `y_mode` transforms:

| Mode | Y-axis | Reference line |
|------|--------|---------------|
| `"percent"` | `% of baseline` | 100 |
| `"log10_percent"` | `log10(percent_change)` | `log10(100)` |
| `"signed_log10_delta"` | `sign(%-100) * log10(|%-100|+1)` | 0 |
| `"log2_fc"` | `log2(rate / baseline)` | 0 |

```{r asp-single-custom, eval = FALSE}
plot_asp_single_protocol(
  asp,
  key_match = "standard_puff",
  y_mode    = "signed_log10_delta",
  #y_lim     = c(-1.5, 1.5),
  heat_dt   = 0.25,
  save_png  = TRUE,
  png_path  = "figs/exp_single_heat"
)
```

## 4b. Concatenated protocols — `plot_asp_concatenated()`

Concatenates all protocols into one global time axis with gaps, producing
a panoramic view of the entire recording.

```{r asp-concat, eval = FALSE}
plot_asp_concatenated(
  asp,
  gap_s    = 2,
  order_by = "wrapped_sweeps",
  y_mode   = "log2_fc",
  y_lim    = c(-1, 1)
)
```

## 4c. Side-by-side baseline vs wash — `plot_sidebyside_heat_wash()`

Combines two `plot_asp_single_protocol()` outputs (baseline and wash
protocol) into a two-column layout.

```{r sidebyside, eval = FALSE}
plot_sidebyside_heat_wash(
  srt,
  y_mode = "log2_fc",
  y_lim  = c(-2, 1),
  heat_dt = 1
)
```

---

# 5. Full figure pipeline — `run_asp_figs_pipeline()`

For batch processing, `run_asp_figs_pipeline()` wraps the concatenated
and single-protocol plots in one call and attaches results to the srt nnest.

```{r fig-pipeline, eval = FALSE}
srt$figs <- run_asp_figs_pipeline(
  srt,
  make_concat_plot  = TRUE,
  make_single_plots = TRUE,
  concat_args = list(y_mode = "log2_fc", y_lim = c(-1, 1)),
  single_args = list(y_mode = "log2_fc", save_png = FALSE)
)

# Access individual plots
srt$figs$asp$concat$plot
srt$figs$asp$single[["Standard_Puff_001"]]$plot
```

---

# Session info

```{r sessioninfo}
sessionInfo()
```
